### 2017-06-13 R/NHTS.Rmd
Created moves-json.R
This script will parse JSON data from Moves for a study by Maggie

```{r libs, eval = TRUE, echo = FALSE, results = "hide", warning = FALSE, error = FALSE, message = FALSE}
options(repos='http://cran.rstudio.com/')
rm(list=ls())
#install.packages(c("ggplot2","dplyr","openssl","httr", "git2r", "devtools", "roxygen2"))
library("tidyverse")
library("devtools")
#library("reshape2")
#library("plyr")
#library("dplyr")
library("TravelSurvey")
library("ITHIM")
fig.width <- 6 # inches
phi <- (1+sqrt(5))/2 # the golden ratio ;)
```

@@

>>>>

```{r libs, eval = TRUE, echo = FALSE, results = "hide", warning = FALSE, error = FALSE, message = FALSE}
options(repos='http://cran.rstudio.com/')
rm(list=ls())
#install.packages(c("ggplot2","dplyr","openssl","httr", "git2r", "devtools", "roxygen2"))
library("devtools")
library("TravelSurvey")
#library("reshape2")
#library("plyr")
#library("dplyr")
install("~/ITHIM/")
library("ITHIM")
fig.width <- 6 # inches
phi <- (1+sqrt(5))/2 # the golden ratio ;)
```

@@

```{r TravelSurvey, eval = TRUE, fig.width = fig.width, echo = FALSE}
NHTS.ts <- readRDS(file = "~/GHI/R/data/NHTS.TravelSurvey.rds")
NHTS.df <- dplyr::left_join(NHTS.ts@person, NHTS.ts@trip, by = c("houseID","subjectID"))
NHTS.df <- within(NHTS.df, {
    id <- paste0(houseID,"-",subjectID)
    duration <- ifelse(is.na(duration), 0, duration)
    mode <- factor(mode, levels = c("walk","cycle","other"))
    location <- location
})
saveRDS(NHTS.df, file = "~/GHI/R/data/NHTS.df.rds")
```

### 2017-06-13 R/msa.Rmd
Created moves-json.R
This script will parse JSON data from Moves for a study by Maggie

```{r msamsa, eval = TRUE, echo = TRUE, warning = FALSE, error = FALSE, message = FALSE}
msaIDFile <- read.csv(system.file("join2.csv", package = "ITHIM"), stringsAsFactors = FALSE)
msaIDs <- msaIDFile$msaNHTS %>% unique
msaIDs <- msaIDs[!is.na(msaIDs)] %>% as.list
names(msaIDs) <- msaIDs
populationList <- getPopulation(msaIDs)

length(populationList)
names(populationList)
head(populationList, 3)

saveRDS(populationList, file = "~/GHI/R/data/populationList.rds")
```

@@

```{r msa2, eval = TRUE, echo = TRUE, warning = FALSE, error = FALSE, message = FALSE}
totalPop <- lapply(populationList,sum) %>% unlist
totalPop[totalPop %>% order(., decreasing = TRUE)] %>% head(., 3)
msaIDFile %>% filter(msaNHTS %in% c(4472,5602,1602)) %>% select(msaName,msaNHTS) %>% unique
```

>>>>

```{r msamsa, eval = FALSE, echo = TRUE, warning = FALSE, error = FALSE, message = FALSE}
msaIDFile <- read.csv(system.file("join2.csv", package = "ITHIM"), stringsAsFactors = FALSE)
msaIDs <- msaIDFile$msaNHTS %>% unique
msaIDs <- msaIDs[!is.na(msaIDs)] %>% as.list
names(msaIDs) <- msaIDs
FList <- getPopulation(msaIDs)

length(FList)
names(FList)
head(FList, 3)

saveRDS(FList, file = "~/GHI/R/data/FList.rds")
```

```{r msamsa2, eval = TRUE, echo = TRUE, warning = FALSE, error = FALSE, message = FALSE}
NHTS.df <- readRDS(file = "~/GHI/R/data/NHTS.df.rds")
FList <- readRDS(file = "~/GHI/R/data/FList.rds")

formatMeanMatrix <- function(meanTable){
    meanMatrix <- meanTable %>% select(age,sex,mean) %>% ungroup() %>% spread(sex,mean) %>% select(M,F) %>% as.matrix()
    row.names(meanMatrix) <- paste0("ageClass",1:8)
    return(meanMatrix)
}

#msaIDs <- unique(NHTS.df$location)
#msaIDs <- as.character(msaIDs[msaIDs!="-1"])

sampleSize <- NHTS.df %>% group_by(location,sex,age) %>% summarise(n=n_distinct(id))
tripDuration <- NHTS.df %>% group_by(location,mode,sex,age) %>% summarise(total=sum(duration))
foo <- right_join(sampleSize,tripDuration, by = c("location","sex","age")) %>% ungroup() %>% mutate(mean = total/n*7) %>% select(location,mode,sex,age,mean) %>% complete(location,mode,sex,age)

meanByLocationByMode <- lapply(split(foo,foo$mode), function(x) split(x, x$location))

MwtList <- lapply(meanByLocationByMode$walk, formatMeanMatrix)
MctList <- lapply(meanByLocationByMode$cycle, formatMeanMatrix)
RwtList <- lapply(MwtList, function(x) x/x[3,2])
RctList <- lapply(MctList, function(x) x/x[3,2])

meanWalkList <- mapply(function(x,y) sum(x*y/sum(y), na.rm = TRUE), MwtList[msaIDs], FList[msaIDs], SIMPLIFY = FALSE)
meanCycleList <- mapply(function(x,y) sum(x*y/sum(y), na.rm = TRUE), MctList[msaIDs], FList[msaIDs], SIMPLIFY = FALSE)

cbind(data.frame(walk = unlist(meanWalkList)), data.frame(cycle = unlist(meanCycleList)))

```

@@

```{r msa2, eval = TRUE, echo = TRUE, warning = FALSE, error = FALSE, message = FALSE}
totalPop <- lapply(FList,sum) %>% unlist
totalPop[totalPop %>% order(., decreasing = TRUE)] %>% head(., 3)
msaIDFile %>% filter(msaNHTS %in% c(4472,5602,1602)) %>% select(msaName,msaNHTS) %>% unique
```
